\EVOSUITE at the SBST 2017 Tool Competition

### 2017-02-22 papers/sbst17/paper_sbst17.tex
minor fix, and fixed score in conclusion

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
and existing open-source test suites were used as baseline. This paper
describes the results obtained by the \EVOSUITE test generation
tool~\cite{FrA11c} in this competition. Details about the procedure of
the competition, the technical framework, and the benchmark classes
can be found in~\cite{sbst17competition}.  In this competition,
\EVOSUITE achieved an overall score of 1457.3, which was the highest
among the competing and baseline tools.

@@

\EVOSUITE~\cite{FrA11c} is a search-based tool~\cite{GoA_TSE12} that
uses a genetic algorithm to automatically generate test suites for
Java classes. Given the name of a target class and the full Java
classpath (i.e., where to find the compiled bytecode of the class
under test and all its dependencies), \EVOSUITE automatically produces
a set of JUnit test cases that maximise the achieved code
coverage. \EVOSUITE can be used on the command line, or through
plugins for popular development tools such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 5th SBST Java Unit Testing Tool Contest. With
an overall score of 1126.7, \EVOSUITE achieved the highest score of
all tools in the competition.

>>>>

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
and existing open-source test suites were used as baseline. This paper
describes the results obtained by the \EVOSUITE test generation
tool~\cite{FrA11c} in this competition. Details about the procedure of
the competition, the technical framework, and the benchmark classes
can be found in~\cite{sbst17competition}.  In this competition,
\EVOSUITE achieved an overall score of 1457, which was the highest
among the competing and baseline tools.

@@

\EVOSUITE~\cite{FrA11c} is a search-based tool~\cite{GoA_TSE12} that
uses a genetic algorithm to automatically generate test suites for
Java classes. Given the name of a target class and the full Java
classpath (i.e., where to find the compiled bytecode of the class
under test and all its dependencies), \EVOSUITE automatically produces
a set of JUnit test cases aimed at maximising code
coverage. \EVOSUITE can be used on the command line, or through
plugins for popular development tools such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 5th SBST Java Unit Testing Tool Contest. With
an overall score of 1457, \EVOSUITE achieved the highest score of
all tools in the competition.
